Global code motion of congruent instructions

### 2017-04-17 paper.tex
fix section 3.4.1

\subsubsection{Reduce register pressure}
\label{hoist:reg-pressure}
Hoisting upwards will decrease the live-range of its use, if it is a last use (a
kill), but increase the live-range of its definition. Conversely, sinking will
decrease the live-range of the defined register but increase the live-range for
killed operands. If the live-range after code-motion is less than before it will
be moved. Essentially, as long as there is one killed operand, code hoisting
will either decrease or preserve the register pressure.  Similarly, code-sinking
will either decrease or preserve the register pressure as long as there is one
operand killed at most.  Following example explains how code motion of identical
computations can reduce the register pressure.  Consider the following example
where the labels prefixed with 'P' represent the position of instruction in a
basic block (names prefixed with 'B').

@@

After hoisting a0 and a1 are removed and a copy
of a0 as a01 is placed in B0 just before the branch.

In this case, since `b' and `c' are killed in `a0' and `a1', hoisting them will
reduce the register pressure in B3 and B4 because two registers will be freed.

Ideally, it should be okay to hoist all the instructions and a later a
live-range-splitting \cite{cooper1998live} pass should make the right decision
of rematerializing the instruction should it be beneficial to do so. But the
current live-range splitting pass of \LLVM{} is not making the optimial decision
and we have found regressions while hoisting aggressively.

>>>>

\subsubsection{Reduce register pressure}
\label{hoist:reg-pressure}
Hoisting upwards will decrease the live-range of its use, if it is a last use (a
kill), but increase the live-range of its definition. Conversely, sinking will
decrease the live-range of the defined register but increase the live-range for
killed operands. If the live-range after code-motion is less than before it will
be moved. Essentially, as long as there is one killed operand, code hoisting
will either decrease or preserve the register pressure.  Similarly, code-sinking
will either decrease or preserve the register pressure as long as there is one
operand killed at most.  The following example explains how code motion of
identical computations can reduce the register pressure.

@@

After hoisting a0 and a1 are removed and a copy of a0 as a01 is placed in B0
just before the branch. Since `b' and `c' are killed in `a0' and `a1', hoisting
the expressions will reduce the register pressure because two registers will be
freed.

Ideally, it should be okay to hoist all the instructions and a later
live-range-splitting \cite{cooper1998live} pass should make the right decision
of rematerializing the instruction should it be beneficial to do so. But the
current live-range splitting pass of \LLVM{} is not making the optimial decision
and we have found performance regressions while hoisting aggressively.
